scRNAseq benchmark in want of a title

### 2019-05-26 bmc_article.tex
updated manuscript

@@

To estimate the correlation between the first principal components and covariates such as library size, we first fitted a linear model on the subpopulations, and correlated the residuals of this model with the covariate of interest.

>>>>

We next investigated the step of dimensionality reduction, comparing in particular Seurat's PCA, GLM-PCA \citep{townesGlmpca2019}, and a two-step PCA. Seurat's default PCA weighs the cell embeddings by the variance of each component,+

@@

To estimate the correlation between the principal components and covariates such as library size, we first fitted a linear model on the subpopulations, and correlated the residuals of this model with the covariate of interest.
